### 2018-12-01 chapters/3-results.tex
readability

The final model proposed to differentiate PCa low Gleason score and high Gleason
score includes the features from ADCₘ, K and T₂w (listed in S12) and the
expected performance of the model is showed in Figure~\ref{fig:roc}.

>>>>

The final model proposed to differentiate low from high Gleason score PCa
includes the features from ADCₘ, K, and T₂w listed in S12. The expected
performance ROC is presented in Figure~\ref{fig:roc}.
